Phenotype and risk assessment of insect venom anaphylaxis: a case - control study of the European Anaphylaxis Registry

### 2019-10-16 analysis/paper/paper.Rmd
corrected figure 3

Younger patients (under 22) presented even more prominent differences in hypotension symptoms and significantly less frequently reported gastrointestinal symptoms (e.g. vomiting) when the reaction was triggered by insect venom.(Fig. \@ref(fig:figsymptoms)C-E)

@@

We found that `r (skin_symptoms$masto_tab$prop[c(2)]*100) %>% round(1)`% of patients with concomitant mastocytosis had anaphylaxis without skin symptoms (i.e. urticaria and flushing) which was significantly more compared to patients without diagnosed mastocytosis (`r (skin_symptoms$masto_tab$prop[c(1)]*100) %>% round(1)`%, `r pval(skin_symptoms$masto_chisq$p.value)`) and this observarion was most prominently seen in VIA (Fig. \@ref(fig:figskinsymptoms)).

Similarily, in non-mastocytic patients undergoing VIA, urticaria or flushing as symptoms of anaphylaxis were present less often than if anaphylaxis was triggered by other elicitors (`r (skin_symptoms$tab$prop[2]*100) %>% round(1)`% vs `r (skin_symptoms$tab$prop[4]*100) %>% round(1)`% respectively, `r pval(skin_symptoms$chisq$p.value)`). Moreover, in this specific subgroup of patients (i.e. non-mastocytic and at the same time lacking urticaria or flushing) VIA was significantly more frequently severe (`r (skin_symptoms$severe_tab$prop[c(6,2)]*100) %>% round(1) %>% paste0(collapse="% in VIA vs. ")`%, `r pval(skin_symptoms$masto_chisq$p.value)`% in non-VIA).

@@

```{r figskinsymptoms, fig.cap="Lack of skin symptoms during anaphylaxis is associated with more severe IVA.", fig.height=5}
fig_skinsymptoms
```

>>>>

Younger patients (under 22) presented even more prominent differences in hypotension symptoms and significantly less frequently reported gastrointestinal symptoms (e.g. vomiting) when the reaction was triggered by insect venom (Fig. \@ref(fig:figsymptoms)C-E).

@@

We found that `r (skin_symptoms$masto_tab$prop[c(2)]*100) %>% round(1)`% of patients with concomitant mastocytosis had anaphylaxis without skin symptoms (i.e. urticaria and flushing) which was significantly more compared to patients without diagnosed mastocytosis (`r (skin_symptoms$masto_tab$prop[c(1)]*100) %>% round(1)`%, `r pval(skin_symptoms$masto_chisq$p.value)`) and this observarion was most prominently seen in VIA.

Similarily, in non-mastocytic patients undergoing VIA, urticaria or flushing as symptoms of anaphylaxis were present less often than if anaphylaxis was triggered by other elicitors (`r (skin_symptoms$tab$prop[2]*100) %>% round(1)`% vs `r (skin_symptoms$tab$prop[4]*100) %>% round(1)`% respectively, `r pval(skin_symptoms$chisq$p.value)`). Moreover, in this specific subgroup of patients (i.e. non-mastocytic and at the same time lacking urticaria or flushing) VIA was significantly more frequently severe (`r (skin_symptoms$severe_tab$prop[c(6,2)]*100) %>% round(1) %>% paste0(collapse="% in VIA vs. ")`%, `r pval(skin_symptoms$masto_chisq$p.value)`% in non-VIA,  Fig. \@ref(fig:figskinsymptoms)B).

@@

```{r figskinsymptoms, fig.cap="Lack of skin symptoms (i.e. urticara and flushing) during anaphylaxis is associated with more severe IVA. A: lack of skin symptoms and mastocytosis in VIA and non-VIA cases. B: Lack of skin symptoms according to severirty in both anaphylaxis groups. C: Relation of reaction severity according to the elicitor and the absence of skin symptoms in relation to categorized BST values. D: Continous values of BST according to severity in both non-VIA and VIA with subgrouping to skin symptoms.", fig.height=5}
fig_skinsymptoms
```
